---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# howzatR

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/howzatR)](https://CRAN.R-project.org/package=howzatR)
<!-- badges: end -->

The goal of howzatR is to provide useful functions for cricket analysis & exploratory.

## Installation

You can install a stable version of howzatR using R/Rstudio with:

``` r
install.packages("howzatR")
```

You can install the development version of howzatR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lukelockley/howzatR")
```

## Example - Batters Analysis

This is a basic example how to use the batting functionality:

```{r example - batters analysis}
library(howzatR)
library(dplyr)

## Basic Batting dataset
bat_raw_df


## Analysis
bat_df <- bat_raw_df %>%
  mutate(
    Outs = Inns - NO,
    Average = bat_avg(runs_scored = Runs_Scored, no_dismissals = Outs),
    Strike_Rate = bat_sr(runs_scored = Runs_Scored, balls_faced = Balls_Faced)
  )

## Results
bat_df
```

## Example - Bowling Analysis

This is a basic example how to use the bowling functionality

```{r example - bowling analysis}
library(howzatR)
library(dplyr)

## Basic Bowling dataset
bowl_raw_df


## Analysis
bowl_df <- bowl_raw_df %>%
  mutate(
    Economy = bowl_econ(balls_bowled = Balls_Bowled, runs_conceded = Runs_Conceded),
    Average = bowl_avg(runs_conceded = Runs_Conceded, wickets_taken = Wickets),
    Strike_Rate = bowl_sr(balls_bowled = Balls_Bowled, wickets_taken = Wickets),
    Overs = balls_to_overs(balls = Balls_Bowled)
  ) %>%
  select(
    Player, Balls_Bowled, Overs, Runs_Conceded,
    Wickets, Economy, Average, Strike_Rate
  )

## Results
bowl_df
```
